---
name: Ricky
surname: Woznichak
position: "MSDM | Digital Marketing and Sales Professional"
phone: +1 (323) 383-5876
www: rickywoz.netlify.app
email: "woznichak@gmail.com"
github: your-github
linkedin: rickywoznichak
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::latexcv:
    theme: classic
header-includes:
   - \usepackage{enumitem}
   - \setlist[itemize]{nosep, left=0pt}
   - \setlist[enumerate]{nosep, left=0pt}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

if (!requireNamespace(c("tinytex","vitae","tibble"), quietly = TRUE)) {
  install.packages(c("tinytex","vitae","tibble"))
}

if (Sys.which("pdflatex") == "" && !tinytex::is_tinytex()) {                    
  message("► TinyTeX not found – installing")
  tinytex::install_tinytex()        
} else {
  message("✓ LaTeX present – no installation needed.")
}

library(vitae)
library(tibble)
```

# Professional Summary

Dynamic digital marketing professional with agency and in-house experience across media planning, branded content, and campaign optimization. After launching my career with top brands like Sony, UMG, and Studio71, I pursued acting full-time—joining SAG and appearing on HBO’s Insecure—while substitute teaching for LAUSD. Currently enrolled full-time in the Master of Science in Digital Marketing program at Cal Poly Pomona (graduating August 2025), I have updated my skillset to meet the demands of today’s evolving digital marketing landscape, with advanced training in SEO, analytics, and performance strategy.

# Technical Skills

- **Programming Languages:** R, SQL  
- **Web Technologies:** HTML, CSS/SCSS, Quarto, HubSpot, Tableau
- **Certifications:** Google Analytics, HubSpot

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ College, ~ Institution,
  "Master of Science in Digital Marketing", "2024 – 2025", "Singelyn Graduate School of Business", "Cal Poly Pomona",
  "Bachelor of Science in Marketing Management", "2002 – 2010", "College of Business Administration", "Cal Poly Pomona"
) %>%
  detailed_entries(Degree, Year, College, Institution)
```

# Honors
- Beta Gamma Sigma Honors Society
- MSDM 2025 "Student of the Year"

# Relevent Work Experience

```{r}
library(tibble)
library(dplyr)

tribble(
  ~years, ~company, ~duties, ~title,

  "9.2024 – 2.2025",
  "John Franklin Insurance - Farmers Insurance Broker",
  list(
    "Developed and managed email marketing and social media campaigns to build brand awareness, nurture leads, and drive conversions.",
    "Monitored performance metrics to optimize campaigns for maximum ROI."
  ),
  "Digital Marketing Manager",

  "9.2012 – 4.2013",
  "Studio 71",
  list(
    "Coordinated development of branded entertainment video content for a top-tier YouTube multi-channel network.",
    "Managed production schedules, asset delivery, and interfaced with a variety of clients including Taco Bell, Gillette, Sony Pictures, Activision, and Sprint by delivering proposals, media plans, and reporting."
  ),
  "Sales Development Coordinator",

  "4.2011 – 9.2012",
  "Universal McCann (UM)",
  list(
    "Planned, launched, and maintained digital media campaigns for Sony Television and Sony Home Entertainment.",
    "Communicated daily and negotiated contracts with media partners and vendors. Reported to studio clients and partners with regular campaign status updates."
  ),
  "Associate Digital Media Planner",

  "6.2010 - 1.2011",
  "Universal Music Group",
  list(
    "Managed online marketing and promotional campaigns for UMG artists and initiatives including Lady Gaga, Taylor Swift, Kid Cudi, Mariah Carey, Jimmy Eat World, and many others.",
    "Collected performance data and presented campaign results to UMG record label executives. Coordinated and delegated campaign tasks to interns."
  ),
  "Digital Marketing Coordinator",

  "1.2010 - 6.2010",
  "Warner Music Group",
  list(
    "Supported the digital sales team by analyzing streaming data, optimizing revenue opportunities, and assisting in partnership strategies to drive sales growth."
  ),
  "Digital Sales Intern",

  "6.2009 - 12.2009",
  "Universal Music Group",
  list(
    "Assisted in executing digital marketing campaigns, analyzing audience engagement, and optimizing content strategies to enhance artist/brand visibility."
  ),
  "Digital Marketing Intern"
) |>
  detailed_entries(
    what = title,
    when = years,
    with = company,
    why = duties
  )


```
